ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/impl.tex
edits
Missing ref

In this section we discuss practical aspects of ShrinkNets, including the
neuron removal  process and several additional optimizations.

@@

\textbf{Threshold strategy}: Under this strategy neurons are removed based on
a fixed threshold expressed in terms of its absolute value. This is the method
used by deep compression \cite{}. We found this method is very sensitive to the initializaiton 
and not robust to noise in the gradients---which occurs commonly when training networks with
stochastic gradient descent---because the threshold depends on the scale of
each weight.

>>>>

In this section we discuss practical aspects of \shrink{}, including 
neuron removal  and several optimizations.

@@

\textbf{Threshold strategy}: Under this strategy neurons are removed based on
a fixed threshold expressed in terms of its absolute value. This is the method
used by deep compression \cite{Han2015}. We found this method is very sensitive to the initializaiton 
and not robust to noise in the gradients---which occurs commonly when training networks with
stochastic gradient descent---because the threshold depends on the scale of
each weight.
